% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%

% Put edit comments in a really ugly standout display
\usepackage{xcolor} 
\usepackage{ifthen}
\usepackage{amssymb}
\usepackage{graphicx}
 
\newboolean{showcomments}
\setboolean{showcomments}{true} % toggle to show or hide comments
\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[2]{
    \fcolorbox{gray}{yellow}{\bfseries\sffamily\scriptsize#1}
    {$\blacktriangleright$#2$\blacktriangleleft$}
   }
   \newcommand{\version}{\emph{\scriptsize$-$working$-$}} 
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\version}{} 
  }
 
\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum} 

% for comments
\newcommand\levi[1]{\nb{Levi}{\textcolor{teal}{#1}}}
\newcommand\salman[1]{\nb{Salman}{\textcolor{blue}{#1}}}
\newcommand\ch[1]{\nb{Chih-Hong}{\textcolor{red}{#1}}}
\newcommand\mav[1]{\nb{Mav}{\textcolor{black}{#1}}}

\usepackage{makeidx}  % allows for indexgeneration
%
\begin{document}
%
\frontmatter          % for the preliminaries

\mainmatter              % start of the contributions
%
\title{EARS-CTRL: From Natural Language to Controller Code in 1 Click}
%
\titlerunning{}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Levi L\'ucio\inst{1} \and Salman Rahman\inst{1}
 \and Saad Bin Abid\inst{1} \and Alistair Mavin\inst{2}}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{}
%
\institute{
fortiss GmbH\\
Guerickestra\ss e 25, 80805 M\"unchen\\
\email{\{lucio,abid\}@fortiss.org, salman.rahman@tum.de}\\
\and
Rolls-Royce, PO Box 31, Derby, UK\\
\email{alistair.mavin@rolls-royce.com}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
Abstract here\ldots
\end{abstract}

\input{text_paper/introduction.tex} 

\input{text_paper/highlights.tex}

\input{text_paper/architecture.tex}

\input{text_paper/relatedwork.tex}

\input{text_paper/limitationsfuturework.tex}

\input{text_paper/conclusion.tex}

%
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}

\end{document}
