\section{Introduction}

The ultimate goal in human-computer interaction is that humans can ``explain''
to computers their needs, using human-centered languages (ideally natural
language). Computers will then perform the actions that will satisfy
those needs. This trend can be observed to be on the rise with automated
call-centers or personal assistants that, through voice commands, can
automatically search for itineraries, restaurants, hotels and even perform
online bookings.

In this paper we describe the \textsf{EARS-CTRL} tool for building and verifying
software controllers. \textsf{EARS-CTRL} has as starting point the EARS (Easy
Approach to Requirements Syntax) language which was created at
Rolls-Royce to improve gathering natural language requirements~\cite{EARS09}.
The language can be seen as ``gently'' constrained English. Through the use of a
small number of patterns, or formatted sentences, EARS copes well with large requirements
specifications for several domains~\cite{EARS10,EARS16}. It has additionally
been shown that using EARS is an effective way for reducing or, in some cases,
eliminating many of the problems that plague requirements documents written
using unconstrained natural language~\cite{EARS09}.

With the \textsf{EARS-CTRL} tool we attempt a step in the direction of
controller construction by using natural language as a central specification
artifact. After specifying the vocabulary to be used in the specification, a
requirements engineer writes the specification using EARS templates. Then, at
the press of a button the controller is synthesized. By using intuitive
simulation and test case generation panels the requirements engineer can
immediately experiment with and validate the controller by providing inputs and
observing the resulting outputs.

This paper is a follow-up of the article~\cite{LucioRCM17}, where we describe a
previous version of the \textsf{EARS-CTRL} tool.
Our new contributions are a revision of the requirements language of
\textsf{EARS-CTRL} which is fully aligned with the original EARS -- by better
covering the semantic gap between EARS and the underlying logical formalism for
controller synthesis. We now also offer the possibilities of simulating 
requirements specifications and of generating test cases.

The \textsf{EARS-CTRL} tool as well as a set of examples other than the ones we
present in this paper is freely available at a GitHub project at \ldots.

% \levi{Talk about the rise of AI in program synthesis and formal methods and how
% we enable requirements engineers to get closer to get closer to a code-free
% program synthesis by providing an appropriate IDE} 
% 
% Note that the front-end of
% the tool is based on the MPS (Meta-Programming System) meta-editor.

% The contributions of this paper are:
% \begin{itemize}
%   \item EARS syntax:
% \begin{itemize}
%   \item components are now devices that can have sensors and actuators and are
%   described in the glossary. This makes it for a more fluid English description. 
%   \item until clauses have been removed from templates. 
% \end{itemize}
% \item{Synthesis}
% \begin{itemize}
%   \item lifting of error codes from the synthesizer. 
% \end{itemize}
% \item Simulation and test case generation.
% \begin{itemize}
%   \item interaction with simulink for simulation.
%   \item interaction with simulink for text case generation
% \end{itemize}

%\end{itemize}